SunPy - Python for Solar Physics

### 2014-08-26 2-1-Map.tex
Some words on metadata.
Add an example of metadata persistance.

The \texttt{Map} class stores all of the metadata retrieved from the header of
the image file in the \texttt{meta} attribute and provides convenience 
properties for commonly accessed metadata: e.g., \texttt{instrument}, 
\texttt{wavelength} or \texttt{coordinate\_system}. 
Listing \ref{code:aia_1} demonstrates the quick-look functionality of 
\texttt{Map}.

>>>>

The \texttt{GenericMap} class stores all of the metadata retrieved from the header of
the image file in the \texttt{meta} attribute and provides convenience 
properties for commonly accessed metadata: e.g., \texttt{instrument}, 
\texttt{wavelength} or \texttt{coordinate\_system}.
These properties are dynamic mappings to the underlying metadata and all methods 
of the \textit{GenericMap} class modify the meta data where needed.
For example, if \verb|aiamap.meta[`instrume']| is modified then \verb|aiamap.instrument| 
will reflect this change.
Currently this is implemented by not preserving the keywords of the input data,
instead modifying meta data to a set of ``standard" keys supported by SunPy.
Listing \ref{code:aia_1} demonstrates the quick-look functionality of 
\texttt{Map}.
